---
title: "linreg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linregpackage)
```
##description

The linreg package have the two arguments formula and data. The package calculates: regressions coefficients, the fitted values, the residuals, the degrees of freedom, the residual variance, the variance of the regression coefficients, the t-values for each coefficient.


##methods

print()
The function print() print out the coefficients and coefficient names

plot() 
The function plot() the following two plots using ggplot2

resid() 
The function resid() plot return the vector of residuals

coef() 
The function coef() return the coefficients as a named vector

summary() 
The function return a similar printout as printed for lm objects


##Examples

linreg_obj<-linreg$ new(formula=Petal.Length ~ Species,data=iris)

linreg_obj$ formula

linreg_obj$ t_value

linreg_obj$ resid()

linreg_obj$ pred()

linreg_obj$ coef()

linreg_obj$ print()

linreg_obj$ plot()

linreg_obj$ summary()

linreg_obj$ B_h_var
